Paper Visualizations

### 2022-05-25 eda/paper-graphics.Rmd
updated tables

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, error = F)
library(tidyverse)
library(ggplot2)
library(boxr)
library(stargazer)
box_auth()

@@

@@

author_types$position <- ifelse(author_types$position == "auf", 'Reproductive Rights', 'Antiabortion')
author_types <- author_types %>% mutate(`Amicus Author Type` = case_when(
  author_type == 'chc' ~ 'Feminist Organizations',
  author_type == 'lif' ~ 'Anti-Feminist Organizations',
  author_type == 'med' ~ 'Medical Practioners/Orgs/Researchers/Educators',
  author_type == 'leg' ~ 'Legal Organizations',
  author_type == 'rel' ~ 'Religious Groups',
)) %>% select(-author_type)

@@

#add totals
total <- c("Total", sum(author_table$`Reproductive Rights`), sum(author_table$`Antiabortion`))
author_table <- rbind(author_table, total)

#create table
stargazer(author_table, summary=FALSE, rownames=FALSE, title = "Table 1.  Total Number of Amicus Briefs by Amicus Type in the Supreme Court Abortion Cases", notes = "a. Legal cases can have more than one amicus type filed in a case (e.g., differing groups of feminist organizations can file more than one brief in a case).  Also, the same organizations file briefs in multiple cases.", header=FALSE, type = 'html', notes.align = 'l', out = "graphics/table1.htm")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, error = F)
library(tidyverse)
library(ggplot2)
library(boxr)
library(stargazer)
library(stringi)
box_auth()

@@

other_types <- amicus %>% select(forgau, antauo, govauf, govauo, sg, racauf, racauo, mpeauf, mpeauo, lg_bauf, forgauf, aclauf, aclauo, sgauf, sgauo) %>%
  mutate(across(where(is.character), as.numeric)) %>%
  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE))) %>%
  pivot_longer(.,cols = c(forgau, antauo, govauf, govauo, sg, racauf, racauo, mpeauf, mpeauo, lg_bauf, forgauf, aclauf, aclauo, sgauf, sgauo), names_to = "var", values_to = "ct") %>%
  arrange(var)

@@

author_types$position <- ifelse(author_types$position == "auf", 'Reproductive Rights', 'Antiabortion')
author_types <- author_types %>% mutate(`Amicus-Author Type` = case_when(
  author_type == 'chc' ~ 'Feminist Organizations',
  author_type == 'lif' ~ 'Prolife Organizations',
  author_type == 'med' ~ 'Medical Organizations',
  author_type == 'leg' ~ 'Legal Organizations',
  author_type == 'rel' ~ 'Religious Groups',
)) %>% select(-author_type)

@@

#create other category
other_types <- other_types %>% mutate(position = stri_sub(var,-1))
other_types$position <- ifelse(other_types$position == 'f', 'Reproductive Rights', 'Antiabortion')
other_types <- other_types %>% group_by(position) %>% summarize(ct = sum(ct))
other <- other_types %>% pivot_wider(names_from = position, values_from = ct)
author_table <- rbind(author_table, c("Other", other$`Reproductive Rights`, other$`Antiabortion`))

#add totals
total <- c("Total", 330, 441)
author_table <- rbind(author_table, total)

#manually order
author_table$order <- c(1, 4, 2, 3, 5, 6, 7)
author_table <- author_table %>% arrange(order) %>% select(-order)

#create table
stargazer(author_table, summary=FALSE, rownames=FALSE, title = "Table 1.  Total Number of Amicus Briefs by Amicus-Author Type in the Supreme Court Abortion Cases", notes = c("a. The “Other” category contains various additional types of amici, including for organizations focused on racial justice and LGBTQ rights and from the U.S. Solicitor General.", "b. The separate amicus categories do not sum to the column totals because amicus briefs can be counted in more than one category."), header=FALSE, type = 'html', notes.align = 'l', out = "graphics/table1.htm")
```
